Embracing the Laws of Physics: \\ Reversible Models of Computation

### 2017-11-28 survey/survey.tex
more on structure with some speculative sections

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
%\pagestyle{headings}
\bibliography{cites}
\end{document}

>>>>

All programs/proofs/deductions are  
isomorphisms/equivalences/deformations.

Take it as a fundamental principle; avoid detour via irreversible
functions and current models of computations.

@@

sound and complete isomorphisms for finite types

name the isomorphisms

\begin{verbatim}
examples: 
  (1 + 1) x ((1 + 1) x b) = (b+b) + (b+b)
  conditionals
  toffoli
  fredkin
\end{verbatim}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data IV: Recursive Types}

Add recursion to structured finite types, trace, feedback, loop...

Natural numbers: fold/unfold

Partial isos

meta-circular interpreter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data V: Exclusive Disjunctions}

???

Quantum over finite field

@@

CS abstractions are based on ``old'' physics

computer applications are more and more ``physical''

physical principles such as conservation of information should be part
of our foundational abstractions

quest for other principles; other data models; graphs; HoTT

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Acknowledgements} many students and colleagues

\bibliographystyle{plainnat}
%\pagestyle{headings}
\bibliography{cites}
\end{document}
